The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-07-18 paper.tex
Added some basic data

>>>>

\subsection{Data}

Irish epenthesis targets sonorant-initial clusters and occurs both across syllable boundaries and in codas.  The epenthetic vowel is [\textipa{@}] in nonpalatalised environments and [i] otherwise \citep{ni.chiosain.1999}.

\ex. \a. /alb\textipa{@}/ $\rightarrow$ [al\textipa{@b@}] \\
         {\it Alba} `Scotland'
     \b. /dorx\textipa{@}/ $\rightarrow$ [dor\textipa{@x@}] \\
         {\it dorcha} `dark'
     \b. /gorm/  $\rightarrow$  [gor\textipa{@}m] \\
         {\it gorm} `blue'
     \b. /banb\textipa{@}/ $\rightarrow$ [ban\textipa{@b@}] \\
         {\it Banba} `a name for Ireland'
     \b. /kon\textipa{f@}/ $\rightarrow$ [kon\textipa{@f@}] \\
         {\it confadh} `anger'
     \b. /an\textsuperscript{j}m\textsuperscript{j}/ $\rightarrow$ [an\textsuperscript{j}im\textsuperscript{j}] \\
         {\it ainm} `name'
     \z.
     (\citet{carnie.1994}:(37) and \citet{ni.chiosain.1999}:(2))

The pattern of epenthesis outlined above does not apply to onset clusters.  Sonorant-initial clusters
are attested in onsets.

\ex. \a. [\textipa{mna:}] or [\textipa{mra:}] (depending on dialect) \\
         {\it mn\'a} `women'
     \b. [\textipa{m\textsuperscript{j}r\textsuperscript{j}i:ra:n}] \\
         {\it mriath\'an} `sea-rods'
     \z.
     (\citet{swingle.1992}: 456)
